---
title: "Statistical Inference Course project2"
author: "Md Asadul Islam"
date: '2016-05-08'
output: html_document
---
## Overview 
I am going to 

* Load the ToothGrowth data and perform some basic exploratory data analyses
* Provide a basic summary of the data.
* Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. 
* State your conclusions and the assumptions needed for your conclusions.

```{r}
library(ggplot2)
library(datasets)

data(ToothGrowth)

```
## Basic Summary of ToothGrowth data
```{r}
# let's see few data
head(ToothGrowth)

#let see type of data and it's stactures 
str(ToothGrowth)

# let's summarize data
summary(ToothGrowth)
```
Let's do violin plot of Tooth length by Dose and suppement
```{r}

g <- ggplot(data = ToothGrowth, aes(x = factor(dose), y = len, fill = supp))
g <- g + geom_violin() 
g <- g + labs(title = "Violin Plot of Tooth Length by Dose and Supplement"
              ,x = "Dose"
              ,y = "Tooth Length"
              ,fill = "Supplement")
g <- g + geom_boxplot(width = 0.2, position = position_dodge(0.8))
g
```

## Hypothesis test 

