---
title: "Reproducible Research - Course Project 2"
output: html_document
---
## 1-Project Title:
NOAA Storm Database analysis for finding impact on population health and economic consequence

## 2-Synapsis
Storms and other severe weather events can cause both public health and economic problems for communities and municipalities. Many severe events can result in fatalities, injuries, and property damage, and preventing such outcomes to the extent possible is a key concern.

This project involves exploring the U.S. National Oceanic and Atmospheric Administration's (NOAA) storm database. This database tracks characteristics of major storms and weather events in the United States, including when and where they occur, as well as estimates of any fatalities, injuries, and property damag. Here we will find the imact of stroms and other severe weater on Population health and greatest economic consequence.

## 3-Data Preprocessing
#### 3.1-Loading data

```{r}
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2", destfile="Stromdata.csv.bz2" , 
              method="curl", quiet = FALSE, mode = "w",
              cacheOK = TRUE,
              extra = getOption("download.file.extra"))
mydata = read.csv("Stromdata.csv.bz2")
#summary(mydata)
str(mydata)
```
#### 3.2-Subsetting data

```{r}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
